---
title: "Combine two data products"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Combine two data products}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Goal

Combine two data products to demonstrate the workflow


## Background

A data product with a broader scope may encompass one or more other data 
products. In such cases, data products can be directly imported within the data
processing logic and they are not considered `input_data`.


## User Story

We need to have information we derived and encoded previously within 
`dp_cars-us001` and information within `dp_mtcars-us001` (which is simply a toy
data product based on `mtcars` dataset we have built).

## Step 1: Initialize the project

As this is a new project, we initialize the project using `dpbuild::dp_init`. See
the [vignette](https://amashadihossein.github.io/daapr/articles/daapr.html) on 
new project workflow for details of what the initialization does.


```{r dp_init_, eval = F}
library(daapr)

board_params_set_dried  <- fn_dry(board_params_set_s3(board_alias = "<ALIAS>",
                                                      bucket_name = "<BUCKET>",
                                                      region = "<REIGION>"))

# Dry function call to setting credentials
creds_set_dried <- fn_dry(creds_set_aws(key = Sys.getenv("AWS_KEY"),
                                        secret = Sys.getenv("AWS_SECRET") ))

# Initialize dp repo
dp_repo <- dp_init(project_path = "dp_xcars",
                   project_description = "Cars and mtcars combined data product",
                   branch_name = "us001",
                   branch_description = "User story 1",
                   readme_general_note = "Data product combining cars and metcars",
                   board_params_set_dried = board_params_set_dried,
                   creds_set_dried = creds_set_dried)
```


## Step 2: Set up the working environment

At this point your project has all the basic components to provide you with a 
sandbox where you can do your development. It is not necessary, but it may be
instructional to clean and restart your R session before this next step. Then,
activate and set up the sandbox for this project.

```{r setup, eval = F}
setwd(dp_repo)

# only necessary if you re-started your R session
if(!"daapr" %in% (.packages()))
  library("daapr")

# Set up "promised" env variables
Sys.setenv("AWS_KEY" = "<BUCKETS AWS KEY>")
Sys.setenv("AWS_SECRET" = "<BUCKETS AWS SECRET>")

# Retrieve configuration
config <- dpconf_get(project_path = ".")

# Set up remote git env variable so you can directly push your code to git 
# remote. This will only be used when you are pushing the code, but we can set 
# it now as we are setting up our working env. If you don't want to deal with
# this you can skip this. You can still go quite far in the workflow
Sys.setenv("GITHUB_PAT" = "<YOUR GITHUB PAT>")
```

## Step 3: Build the data product

Here is where the main logic of the data product is implement and the data
product is built. Note, if we had additional data that needed to be included in
the data product, we would mapped and synced it as done when building `dp_cars`,
prior to build the `dp_xcars` logic.

```{r dpbuild, eval = F}
dp_connect(board_params = config$board_params, creds = config$creds)

dp_cars <- dp_get(board_params = config$board_params,
                  data_name = "dp-cars-us001")

dp_mtcars <- dp_get(board_params = config$board_params,
                  data_name = "dp-mtcars-us001")

# build your output data
output <- list(cars = dp_cars$input$cars, mt_cars = dp_mtcars$input$mtcars)

# Structure the input, output, metadata ... you wish to have in your data product
data_object <- dp_structure(data_files_read = NULL,
                            output = output, config = config)

# save and log the data product built
dp_write(data_object = data_object, project_path = ".")
```

## Step 5: Commit and push

At this point, you can commit and push your code.
NOTE: for your push to work

1. You should have created the empty repo on the git remote (e.g. github)
2. `Sys.getenv("GITHUB_PAT")` returns the corresponding "GITHUB_PAT"

```{r dpcommit_, eval = F}
dp_commit(project_path = ".", commit_description = "First dp build")
dp_push(project_path = ".")
```

## Step 6: Deploy

The typical deploy should follow a fresh clone from remote git (e.g. by CI), but
here for brevity we can bypass that and manually deploy.

```{r dpdeploy, eval=FALSE}
dp_deploy()
```

## Step 7: Data access

Typical access pattern starts with setting up the env vars, but for brevity 
here we can just use the existing config to connect to the board, get the data 
and list what else is on the board.

```{r dpi_, eval=FALSE}
dp_connect(board_params = config$board_params, creds = config$creds)

dp <- dp_get(board_params = config$board_params, data_name = "dp-xcars-us001")

dp_list(board_params = config$board_params)
```
