---
title: "Update build logic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Update build logic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Goal:

Document workflow for updating the data processing logic. Here, for simplicity 
the input data remains unchanged.

## User story

We are interested in updating the previously built data product `dp-cars-us001` 
so that it provides distances in cars dataset in cm. See [minimalist example](https://amashadihossein.github.io/daapr/articles/min_wrkfl.html) 

## Step 1 Clone the existing `dp_cars` project, set env and activate

Clone existing data product you wish to modify. Navigate to the directory under
which you wish to put the project folder and provide your `GITHUB_PAT` to the 
environment as shown below.

```{r dpclone, eval=FALSE}
# Set up "promised" env variables
Sys.setenv("AWS_KEY" = "<BUCKETS AWS KEY>")
Sys.setenv("AWS_SECRET" = "<BUCKETS AWS SECRET>")
Sys.setenv("GITHUB_PAT" = "<YOUR GITHUB_PAT>")

dp_clone(remote_url = "<GIT PATH/dp_cars.git>", branch = "us001")
renv::activate(project = "./dp_cars/")
# Check if the project is set up correctly
is_valid_dp_repository()
renv::restore()

library(daapr)
# get config
config <- dpconf_get(project_path = ".")
```

## Step 2 Modify `dp_make.R`

Open `dp_make.R` and edit to add a single line 
`dplyr::mutate(dist_cm = 100 *  dist_m)` as shown below:

```{r dp_make_edit, eval=FALSE}
# read in the input data from what is recorded by dpinput_write
data_files_read <- dpinput_read()

# build your ouput data
output <- data_files_read$cars(config = config) %>% 
  dplyr::mutate(dist_m = 0.3048 * dist) %>%
  dplyr::mutate(dist_cm = 100 *  dist_m)

# Structure the input, output, metadata ... you wish to have in your data product
data_object <- dp_structure(data_files_read = data_files_read,
                            output = output, config = config)

# save and log the data product built
dp_write(data_object = data_object, project_path = ".")
```

## Step 4 Build and evaluate

Here we simply source the edited `dp_make.R` and given its simplicity evaluation
is simply confirming that `data_object` is anticipated

```{r build, eval=FALSE}
source("./dp_make.R")
```

You can check your updated data product by inspecting the rds object in the `output_files`
folder before continuing with the next steps.

## Step 5 Commit and push

Commit the changes and push the modified `dp_cars` to remote git repo

```{r dp_com_push, eval=FALSE}
dp_commit(project_path = ".", commit_description = "Added cm feature")
dp_push(project_path = ".")
```

## Step 6 Deploy

Deploy (as well as build) may be done on a different machine (e.g. CI) but for 
brevity here we can just use the local build and deploy manually

```{r deploy, eval=FALSE}
dp_deploy()
```


## Step 7: Data access (optional)

If you wanted to access the from the remote resource, you can simply connect and
and pull the data.

```{r dpi_, eval=FALSE}
dp_connect(board_params = config$board_params, creds = config$creds)

dp <- dp_get(board_params = config$board_params, data_name = "dp-cars-us001")

dp_list(board_params = config$board_params)
```

